## Purpose
The purpose of this code is to analyse the impact of coupon treatment on the amount spent by customers in a retail setting on a given day. We will use a dataset that contains information about customer purchases, including whether they received a coupon and how much they spent.

## Load necessary libraries
```{r}
#install.packages("causalweight")
library(lmtest)
library(sandwich)
library(causalweight)
```

## Regression analysis
```{r}
data(coupon)
results <- lm(dailyspending ~., data=coupon)
coeftest(results, vcov = vcovHC)
``` 

On average customers who received a coupon spent $73.64 more than those who did not receive a coupon, holding all other variables constant. This suggests that the coupon treatment has a positive effect on customer spending. However, it is important to consider potential confounding variables and the overall context of the data before drawing definitive conclusions about causality.

## Matching analysis
```{r}
#install.packages("Matching")
library(Matching)
y <- coupon[,1]; d <- coupon[,2]; x <- as.matrix(coupon[,3:9])
results <- Match(Y=y, Tr=d, X=x, estimand="ATE")
summary(results)
```

Using matching analysis, we find that the average treatment effect (ATE) of receiving a coupon on daily spending is approximately $60, which is less than the regression analysis. This suggests that, on average, customers who received a coupon spent $60 more than those who did not receive a coupon, after controlling for other covariates.

## Matching with Inverse Probability of Treatment Weighting (IPTW)

```{r}
results_iptw <- treatweight(y=y, d=d, x=x)
results_iptw$effect; results_iptw$pval
```

Using Inverse Probability of Treatment Weighting (IPTW), we find that the estimated effect of receiving a coupon on daily spending is approximately $80, with a p-value indicating statistical significance. This suggests that, after accounting for the probability of receiving a coupon based on covariates, customers who received a coupon spent $80 more than those who did not receive a coupon.

## Double Robust Estimation
```{r}
#install.packages("drgee")
library(drgee)
results_dr <- drgee(
    oformula = formula(y~x),
    eformula = formula(d~x),
    elink = "logit"
)
summary(results_dr)
```

The ATE suggests that receiving a coupon increases daily spending by approximately $74.84 with a p-value indicating statistical significance. Although the ATE is different from the previous methods, it still indicates a positive effect of receiving a coupon on daily spending. 

## Graphical representation of the ATE results
```{r}
#install.packages("ggplot2")
library(ggplot2)
ate_results <- data.frame(
    Method = c("Regression", "Matching", "IPTW", "Double Robust"),
    ATE = c(73.64, 60, 80, 74.84)
)
ggplot(ate_results, aes(x=Method, y=ATE, fill=Method)) +
    geom_bar(stat="identity") +
    theme_minimal() +
    labs(title="Average Treatment Effect (ATE) of Coupon on Daily Spending",
         x="Method", y="ATE ($)") +
    theme(legend.position="none")
```